Tropical Andes plant trait data BIEN

### 2025-08-27 code/L0/L0_TropicalAndes_plants_BIEN_traits.Rmd
Small error in output_path name; could not download AllDesired_BIEN_plant_traits, only TropicalAndes

```{r}
source("~/GitHub/neotropical_plants/code/data_summary.R")

@@

# Write data to csv
```{r}
write.csv(AllDesired_BIEN_plant_traits, file.path(output_path,"AllDesired_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_BIEN_plant_traits, file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv"))
```

>>>>

```{r}
source("C:/GitHub_projects/plant-frugivore diversity/neotropical_plants/code/data_summary.R")

@@

# Write data to csv
```{r}
write.csv(AllDesired_BIEN_plant_traits, file.path(output_path_L0,"AllDesired_BIEN_plant_traits.csv"))
write.csv(TropicalAndes_BIEN_plant_traits, file.path(output_path_L0,"TropicalAndes_BIEN_plant_traits.csv"))
```
